Calculating Entropies With Nested Sampling

### 2017-02-28 paper/ms.tex
Bragging about the integral
Call data d

Consider the basic problem of inferring a quantity $\mu$ from
100 observations $\x = \{x_1, ..., x_{100}\}$ whose probability distribution
(conditional on $\mu$) is
\begin{align}
p(x_i | \mu) &\sim \textnormal{Normal}(\mu, 1).
\end{align}
If the prior for $\mu$ is Normal$(0, 10^2)$, then the posterior is
\begin{align}
\mu | \x &\sim \textnormal{Normal}\left(
                                       \frac{1}{100}\sum_{i=1}^{100} x_i,
                                       \left[\frac{10}{\sqrt{10001}}\right]^2
                                       \right).
\end{align}

The result was
\begin{align}
H_{\d} &= 928.80 \pm 0.38.
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential entropy of
$p(\d)$ is $928.80 - 782.017 = 146.79 \pm 0.38$, consistent with the
true value of $146.499$.

\section{Example 2: Measuring the period of an oscillating signal}

@@

\begin{align}
I_{\bphi, \d} &= \iint
                   \int p(\bphi, \boldeta)p(\d | \phi, \boldeta) \, d\boldeta
                        \ln \left[\frac{p(\bphi, \d)}{p(\bphi)p(\d)}\right]
                        \, d\bphi \, d\d \label{eqn:mutual_info3}
\end{align}

>>>>

Consider the basic problem of inferring a quantity $\mu$ from
100 observations $\d = \{d_1, ..., d_{100}\}$ whose
probability distribution (conditional on $\mu$) is
\begin{align}
p(d_i | \mu) &\sim \textnormal{Normal}(\mu, 1).
\end{align}
If the prior for $\mu$ is Normal$(0, 10^2)$, then the posterior is
\begin{align}
\mu | \d &\sim \textnormal{Normal}\left(
                                       \frac{1}{100}\sum_{i=1}^{100} d_i,
                                       \left[\frac{10}{\sqrt{10001}}\right]^2
                                       \right).
\end{align}
The true value of $H_{\d}$, calculated analytically, is $146.499$.

The result was
\begin{align}
H_{\d} &= 928.80 \pm 0.38.
\end{align}
The log-volume of a 100-dimensional ball of radius $10^{-3}$ is
-782.017. Therefore, the measured differential en
\section{Example 2: Measuring the period of an oscillating signal}

@@

\begin{align}
I_{\bphi, \d} &= \iint
  \left(\int p(\bphi, \boldeta)p(\d | \bphi, \boldeta) \, d\boldeta\right)
                        \ln \left[
  \frac{\int p(\bphi, \boldeta)p(\d | \bphi, \boldeta) \, d\boldeta}
{p(\bphi)\int p(\bphi, \boldeta)p(\d | \bphi, \boldeta) \, d\bphi \, \d\boldeta}\right]
                        \, d\bphi \, d\d
\end{align}
It should not be surprising that this is costly.
